MSstatsPTM: Statistical relative quantification of post-translational modifications in bottom-up mass spectrometry-based proteomics

### 2022-07-26 main/MSstatsPTM_Main.tex
Evaluation

\todo{I suggest that you follow the same order as Figure 3, one paragraph per step. Describe each step, and refer to both the figure, the quantity in the equations and the MSstats functions. Specifically: design; data acquisition; data processing and requirements; converters; steps of statistical analysis. I would state upfront that all the extols before last are performed separately for each data type, and not repeat it in later paragraphs}

@@

The evaluations were based on the $MSstatsPTM$, and were performed without imputing missing values or using Empirical Bayes moderation. $MSstatsPTM$ was compared with Anova and Limma. We did not compare to IsobarPTM because it is only applicable to TMT experiments, meaning it could not be applied to our ground truth data. All the evaluations were done at the adjusted p-value cutoff of $\alpha=.05$. More details are in {\bf Supplementary Sec. \ref{supp-sec:experiments}}.

>>>>

\todo{I suggest that you follow the same order as Figure 3 (my suggested version), one paragraph per step. Describe each step, and refer to both the figure, the quantity in the equations and the MSstats functions. Specifically: design; data acquisition; data processing and requirements; converters; steps of statistical analysis. I would state upfront that all the extols before last are performed separately for each data type, and not repeat it in later paragraphs}

@@

We compared the performance of  $MSstatsPTM$ to that of ANOVA and of Limma. Since IsobarPTM is only applicable to experiments with TMT labeling, it could not be applied to the datasets with known ground truth in this manuscript, and was excluded from the comparisons. $MSstatsPTM$ was used without imputing missing values, and without Empirical Bayes moderation. All the evaluations were done at the FDR-adjusted p-value cutoff of \todo{typically adjusted p-values are denoted $q$, and $\alpha$ is left for the unadjusted p-values. E.f., Eq. 12 uses $q$. Could you check the entire manuscript for consistency} $\alpha=.05$. More details are in {\bf Supplementary Sec. \ref{supp-sec:experiments}}.
